%-------------------------
% Resume in Latex
% Author : Gennadii Chursov
% Based off of: https://github.com/sb2nov/resume and https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
% \usepackage{marvosym}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{ 
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\footskip}{5pt}

\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Rishabh Jitendra Pathak} 
    \\ \vspace{6pt}
    \large \textit{Fullstack Developer} 
    \\ \vspace{6pt} 
    \small  
    % \href{tel:+919867632598}{\underline{+91 98676 32598}} 
    % $|$ 
    \href{mailto:rishabhjpathak@gmail.com}{\underline{rishabhjpathak@gmail.com}} 
    \\ \vspace{6pt}
    \href{https://www.linkedin.com/in/rishabhjpathak/}{\underline{LinkedIn}} 
    $|$
    \href{https://github.com/clumsynite}{\underline{GitHub}} 
    $|$
    \href{https://rishabhpathak.vercel.app/}{\underline{Portfolio}}
\end{center}

%-----------SUMMARY-----------
\section*{Summary}
Experienced web developer proficient in ReactJS for frontend development and NodeJS (Express, Koa) for backend development. Eager learner with a passion for exploring new technologies and frameworks to enhance project capabilities. Excited to leverage expertise in ReactJS and NodeJS to contribute to innovative projects and continue expanding skillset.

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Javascript, TypeScript, SQL, NoSQL} \\
     \textbf{Libraries}{: React, NextJS, Express, React Native} \\
     \textbf{Technologies}{: Git, Docker, AWS} \\
     \textbf{Database}{: Postgres, MongoDB, CouchDB, ArangoDB} \\
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Sept. 2022 {--} Present}
      {Serverlane Technologies }{Mumbai, India}
      \resumeItemListStart
        \resumeItem{Developed various Enterprise Management Applications catering to diverse business needs.}
        \resumeItem{Implemented a robust real-time transaction processing system, efficiently handling high-volume financial transactions while maintaining detailed transaction history and logs.}
        \resumeItem{Designed and integrated a comprehensive logging system to capture and store transaction details, ensuring compliance with regulatory requirements and enabling thorough audit trails.}
        \resumeItem{Engineered a modular and extensible architecture, facilitating seamless integration of new payment gateways with minimal core codebase modifications.}
        \resumeItem{Created a user-friendly configuration interface, enabling non-technical users to manage and prioritize payment gateway preferences, thereby reducing developer dependency.}
        \resumeItem{Collaborated with cross-functional teams to gather requirements and ensure the system met the diverse needs of different projects and business scenarios.}
        \resumeItem{\textbf{Tech Stack: }{ReactJS, NextJS, ExpressTS, AWS Services}}
        \resumeItem{\textbf{Database: }{PostgresQL, MongoDB}}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Jan. 2021 {--} Aug. 2022}
      {Tidal Wave Technologies Pvt. Ltd}{Mumbai, India}
      \resumeItemListStart
        \resumeItem{Collaborated with a team of developers and designers to translate wireframes and functional documentation into responsive and user-friendly UI components using ReactJS.}
        \resumeItem{Assisted in the development and implementation of a farming assistance system designed to streamline agricultural processes and improve productivity for farmers.}
        \resumeItem{Contributed to the design and implementation of an intuitive web-based admin console using ReactJS, enabling administrators to efficiently manage and monitor multiple farms.}
        \resumeItem{Participated in the development of a cross-platform mobile application using React Native, providing farmers with a user-friendly interface for farm-related activities.}
        \resumeItem{Collaborated with senior developers to gather requirements, troubleshoot issues, and implement enhancements to the system.}
        \resumeItem{Engaged in ongoing learning and professional development opportunities to expand technical skills and knowledge in software development.}
        \resumeItem{\textbf{Tech Stack: }{ReactJS, React Native, KoaJS}}
        \resumeItem{\textbf{Database: }{CouchDB, PouchDB, ArangoDB}}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tilak Maharashtra Vidyapeeth }{Pune, Maharashtra, India}
      {Bachelor of Computer Applications}{2017 - 2020}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
